Visual Analysis of Ligand Trajectories in Molecular Dynamics

### 2018-09-27 paper.tex
correction
Revert "correction"
This reverts commit 4119588cf6b5c7eb4c8de44464d2675d5b4d8f52.

%% Abstract section.
\abstract{
Exploration of protein reactivity with other molecules plays a crucial role in many biochemical research disciplines, including protein engineering and drug design.
In many cases, a small molecule (ligand) reacts with the protein in its deeply buried active site. 
As the ligand has to be transported to this site from the protein outer environment, it is crucial to find a feasible trajectory, which the ligand can follow.
There are several in-silico methods, enabling to calculate potential trajectories. 
They usually produce large ensembles of trajectories which have to be further explored by the biochemists who are trying to assess their relevance. 
This decision is based on many parameters of the trajectories which have to be taken into account.
This makes the exploration very demanding as the biochemists have to analyze the multidimensional data about trajectories.
Without proper visual support, this process is very complicated and time demanding.
In this paper, we introduce our tool for visual analysis of ligand trajectories and their various properties.
The tool has been designed in tight collaboration with the domain experts in order to address their needs as much as possible.
It is composed of several linked views, enabling interactive exploration and filtering of trajectories.
The tool consists of a set of 2D views and the 3D view.
It utilizes the concept of a small multiples for communicating different properties of the trajectories.
Through variety of interaction techniques the system enables users to create and store selections that can be compared and evaluated later.
In both 2D and 3D views, users can either observer the individual trajectories or choose to aggregate the information into a functional boxplot or a density visualization.
%It utilizes the concept of a scatterplot matrix for communicating different properties of the trajectories.
The usefulness of the tool is demonstrated on two case studies, conducted by the collaborating protein engineers.
} % end of abstract

>>>>

%% Abstract section.
\abstract{
Exploration of protein reactivity with other molecules plays a crucial role in many biochemical research disciplines, including protein engineering and drug design.
In many cases, a small molecule (ligand) reacts with the protein in its deeply buried active site. 
As the ligand has to be transported to this site from the protein outer environment, it is crucial to study trajectories, which the ligand can follow.
There are several in-silico methods, enabling to calculate potential trajectories in a protein model.
When these methods are applied in connection with molecular dynamics simulation, usually large ensembles of trajectories are produced.
These trajectories have to be further explored by the biochemists who are trying to assess their relevance and gain insight into the protein function.
During this process many parameters of the trajectories have to be taken into account.
This makes the exploration very demanding as the biochemists have to analyze the multidimensional data about trajectories.
Without proper visual support, this process is very complicated and time demanding.
In this paper, we introduce a novel tool for visual analysis of ligand trajectories and their various properties.
The tool has been designed in tight collaboration with the domain experts in order to address their needs as much as possible.
It is composed of several 2D and 3D linked views, enabling interactive exploration and filtering of trajectories.
%The tool consists of a set of 2D views and the 3D view.
It utilizes the concept of a small multiples for communicating the properties of the trajectories.
Through variety of interaction techniques the system enables users to create and store selections that can be compared and evaluated later.
In both 2D and 3D views, users can either observer the individual trajectories or choose to aggregate the information into a functional boxplot or a density visualization.
%It utilizes the concept of a scatterplot matrix for communicating different properties of the trajectories.
The usefulness of the tool is demonstrated on two case studies, conducted by the collaborating protein engineers.
} % end of abstract
